Wireless smart monitoring energy system: a proof of concept

### 2021-03-16 paper/main.tex
tiny fix
expanding on methods

\section{Methods}
Throughout the development, the communication between the server and the plug has been simulated and tested using PacketSender which is a tool that allows sending a configurable packet through the network. To check the system's traffic and the correct handling of acknowledgments, we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark to filter the traffic by port and type and check the correct retransmission of packets by the server. Finally, the entire system has been tested to check the correct transmission of acknowledgments by the plugs.

\section{System results}
\section{Consumption}
%Qui mettiamo workflow generale con immagine algoritmo

>>>>

\section{Methods}
Throughout the development, the communication between the server and the plug has been simulated and tested using PacketSender. This tool allows the user to define the content of a packet in ASCII format, this is turned into bytes and sent to the specified address and port. For our tests, we specified the content of the packets by writing the JSON object in ASCII format, the type of packet (UDP), and the server's address and port. In particular, we tested the system's traffic and the correct handling of acknowledgments. To do this we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark, a packet analyzer, to check the correct retransmission of packets by the server by first filtering the traffic by port and type. Finally, the entire system has been tested to check the correct transmission of acknowledgments by the plugs.

\section{System results}

\section{Consumption}
%Qui mettiamo workflow generale con immagine algoritmo
